R Notebook

### 2018-10-28 Report/paper-results.Rmd
updated results

**Running the tukey on these???**
There was also a difference between conditions in their pointing performance at the end of the first phase (`r apa_print(aov(abs_error ~ learning.condition, data = sub_sop_all))$statistic$learning_condition`), with both Treadmill VR group and the Desktop group performend significantly worse than the group in the real world.
```{r}
TukeyHSD(aov(abs_error ~ learning.condition, data = sub_sop_all))
```

After the modality switch, we can see a significant difference between groups in distance performance (`r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 4,]))$statistic$learning_condition`) and errors as well (`r apa_print(aov(errors ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 4,]))$statistic$learning_condition`), with groups learning on the treadmill or desktop performing worse than those learning in the real world. This between group difference is still present in the 2nd block of the second phase (block 5) in error rate `r  apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 5)))$statistic` and marginally in distance `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 5)))$statistic`. In the last testing block (block 6), we found no differences among the groups in either error rate `r apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic` nor distance `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`.

@@

### Something about pointing?
```{r}
err_phase <- lmer(abs_error ~ phase*learning.condition + (1 | id/phase), data = sub_sop_all)
car::Anova(err_phase, type = "III")

>>>>

**Running the tukey on these???**
```{r}
aov_point_phase1 <- aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 1,])
```
There was also a difference between conditions in their pointing performance at the end of the first phase (`r apa_print(aov_point_phase1)$statistic$learning_condition`), with real group performing significantly better than the Treadmill VR group `r tukey_report(TukeyHSD(aov_point_phase1), condition = "Treadmill VR-Real", delta_name = "error")` and the Desktop group `r tukey_report(TukeyHSD(aov_point_phase1), condition = "Real-Desktop", delta_name = "error")`.

After the modality switch, we can see a significant difference between groups in distance performance (`r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 4,]))$statistic$learning_condition`) and errors as well (`r apa_print(aov(errors ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 4,]))$statistic$learning_condition`), with groups learning on the treadmill or desktop performing worse than those learning in the real world. This between group difference is still present in the 2nd block of the second phase (block 5) in error rate `r  apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 5)))$statistic` and marginally in distance `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 5)))$statistic`. In the last testing block (block 6), we found no differences among the groups in either error rate `r apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`, nor pointing performance `r apa_print(aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 2,]))$statistic$learning_condition`) but we still see small difference in distance performance `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`.

@@

### Something about pointing?
```{r, echo=F, results='hide'}
err_phase <- lmer(abs_error ~ phase*learning.condition + (1 | id/phase), data = sub_sop_all)
car::Anova(err_phase, type = "III")
